---
title: "Wavelet Analysis in Hydrology"
author: "Quan Cui"
date: "5/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

This file is used for a workshop about how to process wavelet analysis on hydrology/climate data
 
Workshop at Watershed Science & Modelling Laboratory, University of Alberta


## 1. Basic setting
```r
library(WaveletComp)
```

## 2. Make some time series data

First, let's make some time series data to get a better understanding about what time series data is.

```{r}
x = seq(0, 30, 0.1)
x

# This Y1 is a simple periodical data using Sin as the function. Dur to this function, the sata has a period as pi.
Y1 = sin(x)
plot(x, Y1, type = "l", col="red", xlab = "time", ylab = "Y1")
legend("topright", legend = "Y1 = sin(x)", col="red", lty=1, cex=0.8)

# Then we make our 2nd time series data that has half period as Y1
Y2 = sin(2*x)
plot(x, Y2, type = "l", col="blue", xlab = "time", ylab = "Y2")
legend("topright", legend = "Y2 = sin(2x)", col="blue", lty=1, cex=0.8)

# If we add Y1 and Y2 up, we get a new data. What is its period?
Y12 = Y1 + Y2
plot(x, Y12, type = "l", xlab = "time", ylab = "Y1 + Y2")
legend("topright", legend = "Y = sin(x) + sin(2x)", lty=1, cex=0.8)

# This is an increasing trend that we want to add to the time series data.
Y3 = 0.2*x
plot(x, Y3, type = "l", xlab = "time", ylab = "Y3", col=73)
legend("bottomright", legend = "Y3 = 0.2 * x", lty=1, cex=0.8, col=73)

# By adding the trend to Y12, this Y123 may be similar to a real-world time series data, which both has trend and period.
Y123 = Y1 + Y2 + Y3
plot(x, Y123, type = "l", xlab = "time", ylab = "Y1 + Y2 + Y3")
legend("bottomright", legend = "Y' = sin(x) + sin(2x) + 0.1x", lty=1, cex=0.8)

# If we use a package WaveletComp, we can easily use a function to generate periodic data with trend.
# There 'Ychange' has changing periods, from 20 to 100, ends at x = 1000.
library(WaveletComp)
Ychange = periodic.series(start.period = 20, end.period = 100, length = 1000)
plot(Ychange, type = "l", xlab = "time", ylab = "Y")

```


May28, 2021. Markdown trial Version 1.1. Modified in browser.
